Analyzing Strawberry Pricing Strategies Across Canadian Vendors\thanks{Code and data are available at: https://github.com/HeTianning/The-price-of-strawberries}

### 2024-12-03 paper/paper.tex
Correct content format

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Uncertainty Quantification:

  \begin{itemize}
  \tightlist
  \item
    The Bayesian approach provides posterior distributions for each
    parameter, allowing for uncertainty quantification. For example, the
    posterior distribution of ( \beta\_\{\text{vendor}\} ) helps
    quantify the uncertainty around vendor-specific pricing effects.
  \end{itemize}
\item
  Incorporating Prior Knowledge:

@@

    \begin{itemize}
    \tightlist
    \item
      ( \beta\_\{\text{vendor}\} ): Reflects the expectation that most
      vendor effects are close to zero, with some deviations.
    \item
      ( \beta\_\{\text{month}\} ): Captures small but meaningful
      seasonal effects.
    \item
      ( \beta\_\{\text{old\_price}\} ): Represents the assumption that
      higher original prices lead to higher observed prices.
    \end{itemize}
  \end{itemize}
\item
  Handling Sparse Data:

  \begin{itemize}
  \tightlist
  \item
    Bayesian models stabilize estimates when some categories (e.g.,
    certain vendors) have fewer observations. Priors regularize the
    estimates, reducing the risk of overfitting.
  \end{itemize}
\item
  Probabilistic Insights:

  \begin{itemize}
  \tightlist
  \item
    Posterior distributions provide credible intervals, making it easier
    to interpret parameter estimates. For instance, a 95\% credible
    interval for ( \beta\_\{\text{old\_price}\} ) of ({[}0.8, 1.2{]})
    means there is a 95\% probability that the original price effect
    lies within this range.
  \end{itemize}
\end{enumerate}

@@

\caption{\label{tbl-modelresults}Explanatory model based on strawberry
prices}

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{22}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& strawberry price model \\ \midrule %% TinyTableHeader
(Intercept)       & \num{1.52}        \\
& (\num{0.66})      \\
vendorLoblaws     & \num{-0.09}       \\
& (\num{0.63})      \\
vendorMetro       & \num{7.50}        \\
& (\num{0.59})      \\
vendorNoFrills    & \num{-0.81}       \\
& (\num{0.62})      \\
vendorSaveOnFoods & \num{-1.00}       \\
& (\num{0.63})      \\
vendorTandT       & \num{-0.91}       \\
& (\num{0.73})      \\
vendorVoila       & \num{-0.76}       \\
& (\num{0.61})      \\
vendorWalmart     & \num{-0.76}       \\
& (\num{0.63})      \\
month             & \num{0.05}        \\
& (\num{0.04})      \\
old\_price       & \num{0.59}        \\
& (\num{0.01})      \\
Num.Obs.          & \num{44854}       \\
R2                & \num{0.139}       \\
R2 Adj.           & \num{0.137}       \\
Log.Lik.          & \num{-174308.202} \\
ELPD              & \num{-174364.4}   \\
ELPD s.e.         & \num{1452.9}      \\
LOOIC             & \num{348728.7}    \\
LOOIC s.e.        & \num{2905.8}      \\
WAIC              & \num{348728.9}    \\
RMSE              & \num{11.79}       \\
\bottomrule
\end{tblr}

@@

Each coefficient ((\beta)) will have a prior distribution, such as a
normal prior centered at zero, reflecting initial uncertainty about its
effect. For instance, the prior for (\beta\emph{\{\text{vendor}\})
assumes no significant differences between vendors initially, allowing
the data to dominate posterior estimates. The Bayesian framework also
provides posterior distributions for each parameter, which capture
uncertainty and enable credible intervals for inference. For example, a
95\% credible interval for (\beta}\{\text{old\_price}\}) indicates the
range of plausible values for the effect of original prices on current
prices, accounting for uncertainty.

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
hline{5}={1,2,3,4,5,6,7,8,9}{solid, 0.1em, black},
}                     %% tabularray inner close
\toprule
& Unique & Missing Pct. & Mean & SD & Min & Median & Max & Histogram \\ \midrule %% TinyTableHeader
current\_price & 238 & 0 & 7.8 & 12.7 & 0.0 & 5.0 & 290.0 & \includegraphics[height=1em]{tinytable_assets/idmt8er0r82vj37ek89zop.png} \\
old\_price & 200 & 0 & 6.1 & 4.3 & 0.4 & 5.4 & 348.0 & \includegraphics[height=1em]{tinytable_assets/ido1q3pnzjq4gbr9teqt8b.png} \\
month & 8 & 0 & 8.9 & 1.6 & 4.0 & 9.0 & 11.0 & \includegraphics[height=1em]{tinytable_assets/idx5eyfzffe0ymhqp3okzw.png} \\
vendor & N & \% &  &  &  &  &  &  \\
Galleria & 400 & 0.9 &  &  &  &  &  &  \\
Loblaws & 4595 & 10.2 &  &  &  &  &  &  \\
Metro & 15819 & 35.3 &  &  &  &  &  &  \\
NoFrills & 4203 & 9.4 &  &  &  &  &  &  \\
SaveOnFoods & 4531 & 10.1 &  &  &  &  &  &  \\
TandT & 627 & 1.4 &  &  &  &  &  &  \\
Voila & 10549 & 23.5 &  &  &  &  &  &  \\
Walmart & 4130 & 9.2 &  &  &  &  &  &  \\
\bottomrule
\end{tblr}

@@

The primary dependent variable in the model is \texttt{current\_price},
representing the observed price per pound of strawberries. Key
predictors include vendor identity (\texttt{vendor}), original price
(\texttt{old\_price}), sale status (\texttt{sale\_status}), and temporal
trends (\texttt{month}). These variables capture the diverse factors
influencing pricing, such as competitive strategies among vendors,
promotional effects, and seasonal supply-demand dynamics.

The model specification includes normal priors for regression
coefficients ((\beta)) and an exponential prior for the residual
standard deviation ((\sigma)). This setup reflects reasonable
assumptions about the effects of predictors, such as small, centered
effects with moderate variability. For instance, the prior for
(\beta\_\{\text{vendor}\}) assumes no extreme pricing differences
between vendors, while allowing the data to dominate posterior updates.

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Uncertainty Quantification}:

  \begin{itemize}
  \tightlist
  \item
    The Bayesian approach provides posterior distributions for each
    parameter, allowing for uncertainty quantification. For example, the
    posterior distribution of \(\beta_{\text{vendor}}\) helps quantify
    the uncertainty around vendor-specific pricing effects.
  \end{itemize}
\item
  \textbf{Incorporating Prior Knowledge}:

@@

    \begin{itemize}
    \tightlist
    \item
      \(\beta_{\text{vendor}}\): Reflects the expectation that most
      vendor effects are close to zero, with some deviations.
    \item
      \(\beta_{\text{month}}\): Captures small but meaningful seasonal
      effects.
    \item
      \(\beta_{\text{old\_price}}\): Represents the assumption that
      higher original prices lead to higher observed prices.
    \end{itemize}
  \end{itemize}
\item
  \textbf{Handling Sparse Data}:

  \begin{itemize}
  \tightlist
  \item
    Bayesian models stabilize estimates when some categories (e.g.,
    certain vendors) have fewer observations. Priors regularize the
    estimates, reducing the risk of overfitting.
  \end{itemize}
\item
  \textbf{Probabilistic Insights}:

  \begin{itemize}
  \tightlist
  \item
    Posterior distributions provide credible intervals, making it easier
    to interpret parameter estimates. For instance, a 95\% credible
    interval for \(\beta_{\text{old\_price}}\) of \([0.8, 1.2]\) means
    there is a 95\% probability that the original price effect lies
    within this range.
  \end{itemize}
\end{enumerate}

@@

@@

Each coefficient (\(\beta\)) will have a prior distribution, such as a
normal prior centered at zero, reflecting initial uncertainty about its
effect. For instance, the prior for \(\beta_{\text{vendor}}\) assumes no
significant differences between vendors initially, allowing the data to
dominate posterior estimates. The Bayesian framework also provides
posterior distributions for each parameter, which capture uncertainty
and enable credible intervals for inference. For example, a 95\%
credible interval for \(\beta_{\text{old\_price}}\) indicates the range
of plausible values for the effect of original prices on current prices,
accounting for uncertainty.

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
hline{5}={1,2,3,4,5,6,7,8,9}{solid, 0.1em, black},
}                     %% tabularray inner close
\toprule
& Unique & Missing Pct. & Mean & SD & Min & Median & Max & Histogram \\ \midrule %% TinyTableHeader
current\_price & 238 & 0 & 7.8 & 12.7 & 0.0 & 5.0 & 290.0 & \includegraphics[height=1em]{tinytable_assets/idipy3vtsc1mlpgxt8o3o7.png} \\
old\_price & 200 & 0 & 6.1 & 4.3 & 0.4 & 5.4 & 348.0 & \includegraphics[height=1em]{tinytable_assets/idp1xv0vuvfk5ug1wh0mm9.png} \\
month & 8 & 0 & 8.9 & 1.6 & 4.0 & 9.0 & 11.0 & \includegraphics[height=1em]{tinytable_assets/idoylf132wx8wev5gteo4b.png} \\
vendor & N & \% &  &  &  &  &  &  \\
Galleria & 400 & 0.9 &  &  &  &  &  &  \\
Loblaws & 4595 & 10.2 &  &  &  &  &  &  \\
Metro & 15819 & 35.3 &  &  &  &  &  &  \\
NoFrills & 4203 & 9.4 &  &  &  &  &  &  \\
SaveOnFoods & 4531 & 10.1 &  &  &  &  &  &  \\
TandT & 627 & 1.4 &  &  &  &  &  &  \\
Voila & 10549 & 23.5 &  &  &  &  &  &  \\
Walmart & 4130 & 9.2 &  &  &  &  &  &  \\
\bottomrule
\end{tblr}

@@

The primary dependent variable in the model is \texttt{current\_price},
representing the observed price per pound of strawberries. Key
predictors include vendor identity (\(\text{vendor}\)), original price
(\(\text{old\_price}\)), sale status (\(\text{sale\_status}\)), and
temporal trends (\(\text{month}\)). These variables capture the diverse
factors influencing pricing, such as competitive strategies among
vendors, promotional effects, and seasonal supply-demand dynamics.

The model specification includes normal priors for regression
coefficients (\(\beta\)) and an exponential prior for the residual
standard deviation (\(\sigma\)). This setup reflects reasonable
assumptions about the effects of predictors, such as small, centered
effects with moderate variability. For instance, the prior for
\(\beta_{\text{vendor}}\) assumes no extreme pricing differences between
vendors, while allowing the data to dominate posterior updates.
